A novel route to the spontaneous formation of porous crystals via viscoelastic phase separation

### 2016-07-09 crystal-gel/talk_statphys.tex
12 min version for statphys. More stremlined intro, no interruption for citations of other instances of crystallised networks

\institute[iLM]{iLM, Univ. Claude Bernard Lyon 1 and CNRS, France}
\title[crystal gel]{A novel route to the spontaneous formation of porous crystals via viscoelastic phase separation}
\author[M. Leocmach]{Mathieu Leocmach}
\date{30 June 2016}
\titlegraphic{
	\begin{tabu}{X[c]X[c]X[c]}
		\includegraphics[height=3\baselineskip]{presentation/Tsurusawa}&
		\includegraphics[height=3\baselineskip]{presentation/John}&
		\includegraphics[height=3\baselineskip]{presentation/Tanaka}\\
		Hideyo Tsurusawa & John Russo & Hajime Tanaka\\
		U. Tokyo & U. Bristol & U. Tokyo\\
	\end{tabu}

@@

\begin{frame}{Crystallisation}
	\tikzsetnextfilename{whyx}%
	\input{presentation/whyx.pgf}

	\begin{block}{Nucleation}
	\begin{itemize}
		\item 10-1000 molecules $\rightarrow$ difficult to observe
		\item classical nucleation theory (CNT): fluid $\xrightarrow{\text{1 step}}$ crystal
	\end{itemize}
	\end{block}
\end{frame}

@@

>>>>

\institute[iLM]{Univ Lyon, Université Claude Bernard Lyon 1, CNRS, Institut Lumière Matière}
\title[crystal gel]{A novel route to the spontaneous formation of porous crystals via viscoelastic phase separation}
\author[M. Leocmach]{Mathieu Leocmach \hfill{\usebeamerfont{normal text}\texttt{\usebeamercolor[fg]{normal text}\footnotesize @LamSonLeoc\includegraphics[height=1em]{Twitter_Bird}}}\vspace{-\baselineskip}}
\date{18 July 2016}
\titlegraphic{
	\begin{tabu}{X[c]X[c]X[c]}
		\includegraphics[height=3\baselineskip]{presentation/Tsurusawa}&
		\includegraphics[height=3\baselineskip]{presentation/John}&
		\includegraphics[height=3\baselineskip]{presentation/Tanaka}\\
		Hideyo Tsurusawa & John Russo & Hajime Tanaka\\
		U. Tokyo & U. Bristol & U. Tokyo\\
	\end{tabu}

@@

\begin{frame}<1>[label=intro]{How does it crystallise?}
	\begin{description}[Understand]
		\item[Understand] natural phenomena
		\item[Engineer] technological applications
	\end{description}

	\begin{block}{What determines the ensemble properties of crystallites?}
	\vspace{-0.5\baselineskip}\begin{columns}
	\column{0.45\textwidth}%
		\begin{itemize}
			\item polymorph type
			\item shape
		\end{itemize}
	\column{0.45\textwidth}
	\begin{itemize}
			\item spatial arrangement
			\item size distribution
		\end{itemize}
	\end{columns}
	\end{block}

	\begin{itemize}
		\item Not always simple nucleation and growth scenario
		\begin{itemize}
			\item<2> Example: Bergeron process
		\end{itemize}
		\item<2> \structure{More detailed view of the processes needed}
	\end{itemize}
\end{frame}

@@

\againframe<2>{intro}
